Easy as Pi: A Network Coding Raspberry Pi Testbed

### 2016-06-01 testbed.tex

This section will be used to present our Raspberry Pi testbed, but also how
it is set up and configured.

The testbed is depicted in \ref{fig:testbed_setup}. It consists of twenty
Raspberry Pi 1 model B rev 2 (Rasp\_01 to Rasp\_20) and 
ten Raspberry Pi 2 model b V1.1 (Rasp2\_01 to Rasp2\_10).
The Raspberry Pis are each equipped with an ethernet interface (eth0) that are
assigned the \ac{IP} addresses listed in the figure.

@@

@@

>>>>

This section will be used to present a Raspberry Pi testbed and the steps to
install and configure the individual devices.

The testbed is depicted in figure~\ref{fig:testbed_setup}. It consists of twenty
Raspberry Pi 1 model B rev 2 (Rasp\_01 to Rasp\_20) and 
ten Raspberry Pi 2 model b V1.1 (Rasp2\_01 to Rasp2\_10).

The goal is to configure all the devices identically with the same software
and configurations. There are however a few differences between them that we
need to take into account. E.g. hostname and network addresses.

The testbed will be used by students that might need to change how the
devices are work either temporary or permanently. We will illustrate how this
can be accomplished using an overlaying filesystem.

Finally, it should be possible to store data that are generated from
simulations on the memory cards that are in the individual Raspberry Pi.
%We using a overlaying filesystem that 
%We will illustrate
%how that can be done. In the case of temporary changes, it is important that
%all changes can be easily reverted. We put a \ac{RAM} filesystem on top of
%the the root filesystem to .
%the configure the
%devices to behave according to their test specifications. We
%will also present how that might be done.

%their linkings. That could be to change network config

%The goal is to configure all the devices to be as identical as possible. This
%means that it is desired to have the same software on every device, but

The Raspberry Pis are all equipped with an ethernet interface (eth0) and
connected by wire to the university's \ac{LAN}. The university network
administration was provided
the \ac{MAC} addresses of the ethernet interfaces to automatically assign
the devices the desired \ac{IP} addresses as shown in the figure. In a personal
\ac{LAN}, another option could be to manually provide the devices with static
\ac{IP}s.
%that are
%assigned the \ac{IP} addresses in the figure and connected wired to the
%university's \ac{LAN}.

@@

We use standard usb power adapters to power the Raspberry Pis.

@@

To get started, we first need to install an \ac{OS} on the
Raspberry Pis. We have decided to create a common image of Raspbian Linux
for all devices. After the image has been configured it can be written to
a memory card and used in any of the Raspberry Pis. This means that each
device needs a memory card, but it does not matter which card is put into
which device.

It can then be written to a memory card and used in one device
after it has been completely configured

that
can be written to a memory card and

We have decided to go with Raspbian linux~\cite{raspbian} and
to install it on memory cards.

%There exists a number of ways to setup a testbed in a centralized manner.
%E.g. using e.g. \ac{NFS}.

There exists a number of ways to setup a testbed

with multiple devices. We
have decided on a very simple approach of simply instal
